One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent flows

### 2020-09-18 manuscript/manuscript.tex
Flow charts converted to PDF instead of PNG. References updated.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../figures/odt_flow_chart/odt_flow_chart.png} 
	\caption{Structural outline of the ODT code, including its major class objects. For brevity, this diagram makes two simplifications. First, it assumes that diffusive advancement in the \texttt{micromixer} uses an explicit solution method; in practice, users specify either an explicit, semi-implicit, or Strang split method. Second, it implies that all of the eddy events sampled by the \texttt{eddy} object are applied to the domain; in reality, eddy events are filtered through several rejection tests (omitted from this figure for clarity) before acceptance and application to the domain.}
	\label{fig:flowchart}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../figures/data_folder_structure/data_folder_structure.png} 
	\caption{Data folder structure and file locations. Boxes indicate folders and ovals indicate files. For a given simulation, \texttt{caseName} will be replaced with the case name specified in the run script. The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number. The number attached to \texttt{dmp} files indicates the output time step, or ``dump" time, of the data file. These correspond to the order of the time steps listed in \texttt{input.yaml}.}
	\label{fig:data_folder_structure}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../figures/odt_flow_chart.pdf} 
	\caption{Structural outline of the ODT code, including its major class objects. For brevity, this diagram makes two simplifications. First, it assumes that diffusive advancement in the \texttt{micromixer} uses an explicit solution method; in practice, users specify either an explicit, semi-implicit, or Strang split method. Second, it implies that all of the eddy events sampled by the \texttt{eddy} object are applied to the domain; in reality, eddy events are filtered through several rejection tests (omitted from this figure for clarity) before acceptance and application to the domain.}
	\label{fig:flowchart}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../figures/data_folder_structure.pdf} 
	\caption{Data folder structure and file locations. Boxes indicate folders and ovals indicate files. For a given simulation, \texttt{caseName} will be replaced with the case name specified in the run script. The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number. The number attached to \texttt{dmp} files indicates the output time step, or ``dump" time, of the data file. These correspond to the order of the time steps listed in \texttt{input.yaml}.}
	\label{fig:data_folder_structure}
\end{figure}
